---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chdgenesFun

<!-- badges: start -->
<!-- badges: end -->

This package provides a repository of commonly used functions to help parse and manipulate the CHDGENES biobank inventory file. **get() functions** (in general) are designed to be used on the full inventory file and return data.frames of interest by aggregating over the aliquot-level data. **add() functions** (in general) are designed to be used on proband centric data files where each row is a proband of interest (i.e., as obtained from HeartsMart) and return appended columns of interest. Several other commonly used helper functions are also included. Minimal documentation and instruction are provided for this package since its use is expected to be limited to our internal team. The functions (verbs) can be piped in succession to expedite complex queries and the generation of reports. 

## Installation

You can install the development version of chdgenesFun from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Nick243/chdgenesFun")
```

## Example

This basic example highlights the core functionality of the chdgenesFun package:

```{r example, eval=FALSE}
## Read in libraries
library(tidyverse)
library(chdgenesFun)

## Read in sample inventory
chd_df <- read_chdgenes("/users/olljt2/desktop/CHDGENES_SampleData.txt")
 
## Get listing of eligible trios for those sets with probands already shipped for WGS (but not parents)
mydata <- chd_df %>%
  remove_decommissioned() %>%
  get_probands_only() %>%
  get_shipped_wgs() %>%
  add_family_id() %>%
  add_in_trio(., chd_df) %>%
  filter(in_biobank_trio == "Y") %>%
  add_mom_wgs(., chd_df) %>%
  add_mom_total_dna(., chd_df) %>%
  add_dad_wgs(., chd_df) %>%
  add_dad_total_dna(., chd_df) %>%
  filter(is.na(mom_shipped_wgs) & is.na(dad_shipped_wgs)) %>%
  filter(mom_total_avail_qcpass_dna >= 2 & dad_total_avail_qcpass_dna >= 2) %>%
  select(-mom_wgs_ship_date, -mom_wgs_order_id, -dad_wgs_ship_date, -dad_wgs_order_id) %>%
  mutate(mom_shipped_wgs = "N",
         dad_shipped_wgs = "N")
```




